---
title: "Measuring Competitor Threat"
output:
  pdf_document:
    keep_tex: true
  word_document: default
  html_document:
    df_print: paged
date: "2023-05-09"
---
\section{Competitor threat}
Disclaimer: The sales of Solarmax in this script is simulated and is not real, thus the result in this script is different form the result of the true study.


Introduction:
This study suggest that in 2021 Solarmax's biggest competitors are vivint, tesla, sunrun, sunpower, freedom, and semper. Therefore, if Solarmax wants to outcompete its major competitors Solarmax through price competition, quality competition,etc, these companies should be their targets.
The second study, which utilizes the 'hopefulness method/blackbox method', conducts a correlation analysis between competitor performances and regional non-Solarmax-sales weighted by solarmax's reliance of revenue on those regions. This study suggests that prioritize competing with Solarcity, rec, and baker, would gain Solarmax with the most market share which the regions that it sells.
The methodology for computing competitor threat is shown below. The second half of the script includes the correlation analysis that compute which competitor should be treated as primary target if Solarmax wants to raise the market share at its sales area.


Methodology:

The way to measure the threat of competitors has to do with the measurement of the a competitor
company's market shares in different areas. For example, if all of our company’s systems are sold to Area
1 in 2021, but 50% of the solar sales in Area 1 is sold by Competitor A, and 40% of solar sales in
Area 1 is sold by Competitor B, then Competitor A would rank higher than Competitor B in the
ranking of competitors. Since our company has sold systems to many area, which equals to hundreds of zip codes, tens of city,
or several counties, and each area held difference importance to the company, we must quantify
the importance of each area to Solarmax and how each competitor’s share of total system sold to each
area contribute to the competitor’s rank in the competitor’s ranking ladder. In order to assign each
area a score of importance that is objective and non-arbitrary, the score should be derived from a
numerical attribute that not only exists in all areas, but the score must also represents the area's importance to the company.
We chose to use sales reliance (the percentage share of total systems sold by the company but to an designated
area) as a measurement of importance to the company. For an example of how an area's importance interacts with a competitor's market
share in the calculation of competitor threat, if 10% of the company’s total
products are sold in Area A, then the importance of Area A would be 10%. if Competitor A had a market share of 50% in
Area A, competitor A will gain a competitor score of 10%*50%=0.05.
The higher the competitor score the company has in total from all the geographic markets(zip codes), the higher the company is ranked in the
competitor ranking.

Formula for competitor threat calculation:

$T_{i}=\text{Threat level of company i against Solarmax}$

$M_{i}=\text{Markshet share at area i}$

$T_{i}=\text{Solarmax's percentage revenue reliance on area }i$

$$ T_{i} = M_{1}*R_{1} + M_{2}*R_{2} ... M_{i}*R_{i}   $$
The first table below is the total threat level score for major competitors in 2021. Each score is calculated from the formula above. 


```{r, warning = FALSE, message = FALSE}
library(tidyverse)

SCEData <- read_csv("SCE_Interconnected_Project_Sites_2021-09-30.csv")
SDGEData<- read_csv("SDGE_Interconnected_Project_Sites_2021-09-30.csv")

CaliforniaData<-rbind(SCEData,SDGEData)
CaliforniaData<-CaliforniaData %>% dplyr::rename_all(funs(make.names(.)))
CaliforniaData<-CaliforniaData[,-c(28:131)]
CaliforniaData$Customer.Sector <- forcats::as_factor(CaliforniaData$Customer.Sector)
CaliforniaData$System.Size.DC<- as.numeric(as.character(CaliforniaData$System.Size.DC))
CaliforniaData$Technology.Type <- forcats::as_factor(CaliforniaData$Technology.Type)
CaliforniaData$Service.County <- forcats::as_factor(CaliforniaData$Service.County)
CaliforniaData$Service.County = tolower(CaliforniaData$Service.County)
CaliforniaData$Service.City <- forcats::as_factor(CaliforniaData$Service.City)
CaliforniaData$Service.City = tolower(CaliforniaData$Service.City)
```

```{r,warning=FALSE,message=FALSE,echo=FALSE}
# In the last chunk, we knew what top companies have inconsistent titles, so in the codes below, we will use gsub to unify all the titles of the same company.
CompetitorStudy<-CaliforniaData%>%filter(App.Received.Date >= as.Date("2010-01-01") & App.Received.Date <= as.Date("2021-09-30")) %>% filter(Customer.Sector == "Residential") 

CompetitorStudy$Installer.Name = tolower(CompetitorStudy$Installer.Name)

CompetitorStudy$Installer.Name<-gsub("california premier solar","californiaPremierSolar",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("california solar systems","CaliforniaSolarSystems",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("clean energy solutions inc","CleanEnergySolutionsInc",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("energy remodeling","EnergyRemodeling",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("energyservicepartners","energy service partners",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("green convergence","GreenConvergence",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("clean energy solutions inc","CleanEnergySolutionsInc",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("home energy systems","HomeEnergySystems",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("new day solar","NewDaySolar",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("new power","NewPower",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("petersendean","petersen dean",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar 360","solar360",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solaroptimum inc","SolarOptimum",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar permit","SolarPermit",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar service","SolarService",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar solutions","SolarSolutions",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar universie","SolarUniverse",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("Solar watt","SolarWatt",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar west","SolarWest",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solar-360","Solar360",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("solarcitymh","solarcity",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("south west","southwest",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("sun bees ","SunBees",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("sun energy","SunEnergy",as.character(CompetitorStudy$Installer.Name))
CompetitorStudy$Installer.Name<-gsub("sun solar","SunSolar",as.character(CompetitorStudy$Installer.Name))
```


```{r,echo=FALSE,warning=FALSE,echo=FALSE,results=FALSE}
CompetitorStudyData<-CompetitorStudy%>% 
  mutate(Installer = str_extract(Installer.Name, "[[:alnum:]]+"))
solarmax<-CompetitorStudyData %>% filter(grepl('solarmax', Installer))%>% drop_na(System.Size.DC) 
totalsales<-solarmax %>% drop_na(System.Size.DC)%>%filter( App.Received.Date > "2015-01-01")%>% summarise(TotalSystemSize=sum(System.Size.DC))
SolarmaxCityTable<-solarmax %>%  filter( App.Received.Date > "2015-01-01") %>% group_by(Service.City)%>%summarise(Solarmax.City.SZ=sum(System.Size.DC))

SolarmaxCityTable$Solarmax.City.SZ<- sample(SolarmaxCityTable$Solarmax.City.SZ)
##solarmax %>% drop_na(System.Size.DC)%>%filter( App.Received.Date > "2021-01-01")%>% summarise(TotalSystemSize=sum(System.Size.DC))

Weigh<-SolarmaxCityTable [,2] / as.numeric(totalsales[1,1])
SolarmaxCityTable<-data.frame(SolarmaxCityTable,Weigh)

names(SolarmaxCityTable)[names(SolarmaxCityTable) == 'Solarmax.City.SZ.1'] <- 'Weigh'


CompetitorStudyData$Installer.Name<-gsub("1st light energy inc","Firstlight",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("solar optimum","SolarOptimum",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("solar watt","SolarWatt ",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("1st light energy inc","Firstlight",as.character(CompetitorStudyData$Installer.Name))


Competitor.City.Performance<-CompetitorStudyData%>%drop_na(System.Size.DC)%>%filter( App.Received.Date > "2015-01-01") %>%group_by(Installer,Service.City)%>%summarise(sum(System.Size.DC))
Competitor.City.Occupation<-CompetitorStudyData%>%drop_na(System.Size.DC)%>%filter( App.Received.Date > "2015-01-01") %>%group_by(Service.City)%>%summarise(sum(System.Size.DC))
Competitor.City.Performance<- merge(Competitor.City.Performance, Competitor.City.Occupation, by = 'Service.City')



City.Occupation.Ratio<-City.Occupation<-Competitor.City.Performance[,3]/Competitor.City.Performance[,4]

Competitor.City.Performance<-data.frame(Competitor.City.Performance,City.Occupation.Ratio)


colnames(Competitor.City.Performance) <- c("Service.City","Competitor","City.Occupation.SZ","City.Total.SZ","City.Occupation.Ratio")

Competitor.City.Performance<- merge(Competitor.City.Performance, SolarmaxCityTable, by = 'Service.City')

colnames(Competitor.City.Performance) <- c("Service.City","Competitor","Competitor.City.Occupation.SZ","City.Total.SZ","Competitor.City.Occupation.Ratio","Solarmax.City.SZ","Solarmax.Importance")


Proximity<-Competitor.City.Performance[,5]*Competitor.City.Performance[,7]


Competitor.City.Performance<-data.frame(Competitor.City.Performance,Proximity)


Top.Competitor.Table.All.Time<-Competitor.City.Performance%>%group_by(Competitor)%>%summarise(Competitor.Threat=sum(Proximity))%>%arrange(desc(Competitor.Threat))%>%filter(Competitor.Threat >=0.009722035	)

colnames(Top.Competitor.Table.All.Time) <- c("2015-2021 Competitor","Competitor.Threat")

```

```{r,echo=FALSE,message=FALSE,warning=FALSE,echo=FALSE, results=FALSE}
total_sales_post_2021<-solarmax %>%  filter( App.Received.Date > "2021-01-01") %>% group_by(Service.City)%>%summarise(Solarmax.City.SZ=sum(System.Size.DC))%>%summarise(sum(Solarmax.City.SZ))


##solarmax %>% drop_na(System.Size.DC)%>%filter( App.Received.Date > "2021-01-01")%>% summarise(TotalSystemSize=sum(System.Size.DC))
SolarmaxCityTable<-solarmax %>%  filter( App.Received.Date > "2021-01-01") %>% group_by(Service.City)%>%summarise(Solarmax.City.SZ=sum(System.Size.DC))

SolarmaxCityTable$Solarmax.City.SZ <- sample(SolarmaxCityTable$Solarmax.City.SZ)
Weigh<-SolarmaxCityTable [,2] / as.numeric(total_sales_post_2021[1,1])
SolarmaxCityTable<-data.frame(SolarmaxCityTable,Weigh)

names(SolarmaxCityTable)[names(SolarmaxCityTable) == 'Solarmax.City.SZ.1'] <- 'Weigh'


CompetitorStudyData$Installer.Name<-gsub("1st light energy inc","Firstlight",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("solar optimum","SolarOptimum",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("solar watt","SolarWatt ",as.character(CompetitorStudyData$Installer.Name))
CompetitorStudyData$Installer.Name<-gsub("1st light energy inc","Firstlight",as.character(CompetitorStudyData$Installer.Name))


Competitor.City.Performance<-CompetitorStudyData%>%drop_na(System.Size.DC)%>%filter( App.Received.Date > "2021-01-01") %>%group_by(Installer,Service.City)%>%summarise(sum(System.Size.DC))
Competitor.City.Occupation<-CompetitorStudyData%>%drop_na(System.Size.DC)%>%filter( App.Received.Date > "2021-01-01") %>%group_by(Service.City)%>%summarise(sum(System.Size.DC))
Competitor.City.Performance<- merge(Competitor.City.Performance, Competitor.City.Occupation, by = 'Service.City')

City.Occupation.Ratio<-City.Occupation<-Competitor.City.Performance[,3]/Competitor.City.Performance[,4]

Competitor.City.Performance<-data.frame(Competitor.City.Performance,City.Occupation.Ratio)
```

```{r,warning=FALSE,message=FALSE,echo=FALSE}
colnames(Competitor.City.Performance) <- c("Service.City","Competitor","City.Occupation.SZ","City.Total.SZ","City.Occupation.Ratio")

Competitor.City.Performance<- merge(Competitor.City.Performance, SolarmaxCityTable, by = 'Service.City')

colnames(Competitor.City.Performance) <- c("Service.City","Competitor","Competitor.City.Occupation.SZ","City.Total.SZ","Competitor.City.Occupation.Ratio","Solarmax.City.SZ","Solarmax.Importance")


Proximity<-Competitor.City.Performance[,5]*Competitor.City.Performance[,7]


Competitor.City.Performance<-data.frame(Competitor.City.Performance,Proximity)



Top.Competitor.Table.2021<-Competitor.City.Performance%>%group_by(Competitor)%>%summarise(Competitor.Threat=sum(Proximity))%>%arrange(desc(Competitor.Threat))%>% filter(Competitor.Threat > 8.935585e-03)

colnames(Top.Competitor.Table.2021) <- c("2021 Competitor","Competitor.Threat")


```



```{r,echo=FALSE}
Top.Competitor.Table.2021 %>% knitr::kable(. )
Top.Competitor.Table.All.Time %>% knitr::kable(. )

```

\section{Which competitors should Solarmax prioritize targeting?}
```{r}
Competitor.City.Performance$non_solarmax_SZ = (Competitor.City.Performance['City.Total.SZ']-Competitor.City.Performance['Solarmax.City.SZ'])$City.Total.SZ
Competitor.City.Performance$competition<-(Competitor.City.Performance['Solarmax.Importance']*Competitor.City.Performance['non_solarmax_SZ'])$Solarmax.Importance
competitor_frame <- Competitor.City.Performance[,c(2,3,7,9,10)]%>%filter(Competitor %in% Top.Competitor.Table.2021$`2021 Competitor`)
colnames(competitor_frame)<-c('Competitor','Competitor.City.Occupation.SZ','Solarmax.Importance','non_solarmax_SZ','competition')
com_table<-spread(competitor_frame , key = Competitor, value = Competitor.City.Occupation.SZ)

cors<-cor(com_table[, c(4:23)], com_table$competition, use = "pairwise.complete.obs")
cor_table<-as.data.frame(cors)
colnames(cor_table)<-c('correlation')
cor_table%>%arrange(desc(correlation))
```



